Software Citation Principles

### 2016-03-24 sc-principles/software-citation-principles.tex
Re-working astro section slightly

In astronomy \& astrophysics: ASCL~\cite{ascl}, AAS journals  and the joint
AAS/GitHub workshop~\cite{aas-software-index} dedicated to software citation,
indexing and discoverability, and the report from a Birds of a Feather session
organized by the ASCL at the Astronomical Data Analysis Software and Systems
(ADASS) XXV conference~\cite{2015arXiv151207919A}.

@@

Geosciences: Ontosoft~\cite{ontosoft} - A Community Software Commons for the Geosciences. Lots of attention given to the metadata
required to describe, discover and execute research software. NSF geosciences workshop around data lifecycle, management and citation~\cite{nsf-geo-data}. This report includes many recommendations for data citation.
\LJHnote{ The Seismological Research Letters, Electronic Seismologists publishes papers on software.} %text needs to be cleaned up LJH%

>>>>

In astronomy \& astrophysics: The Astronomy Source Code Library (ASCL) ~\cite{ascl}, is a website dedicated to the curation and indexing of software used in the astronomy-based literature. In 2015, the AAS and GitHub co-hosted a workshop~\cite{aas-software-index} dedicated to software citation,
indexing and discoverability and more recently, a Birds of a Feather session was held at the Astronomical Data Analysis Software and Systems (ADASS) XXV conference~\cite{2015arXiv151207919A} which included discussion of software citation.

@@

Geosciences: The Ontosoft~\cite{ontosoft} project describes itself as `A Community Software Commons for the Geosciences'. Lots of attention given to the metadata
required to describe, discover and execute research software. NSF geosciences workshop around data lifecycle, management and citation~\cite{nsf-geo-data}. This report includes many recommendations for data citation.
\LJHnote{ The Seismological Research Letters, Electronic Seismologists publishes papers on software.} %text needs to be cleaned up LJH%
